---
title: "PM Take Home Exam"
author: "Lai Jiang"
date: "7/18/2020"
output:
  pdf_document: 
    latex_engine: xelatex
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Chapter 3 question 15
#a
```{r}
library(MASS)
View(Boston)
attach(Boston)
preds<-names(Boston)[-1]
mods<-list()
stats<-list()
for (i in seq(along=preds)){
  p<-preds[i]
  mods[[i]] <- lm(as.formula(paste0("crim ~ ",p)),data=Boston)
}
stats<-t(sapply(mods, function(x) coef(summary(x))[2,]))
r_squared<-sapply(mods,function(x) summary(x)$r.squared)
stats<-cbind(stats,r_squared)
rownames(stats) <-preds
stats2<-stats[order(abs(stats[,"t value"]),decreasing=TRUE),]
stats2
plot(lm(crim~zn))
plot(lm(crim~nox))
plot(lm(crim~black))
plot(lm(crim~medv))

?pairs

#most demonstrate a statisticall signifcant relationship with crim, except chas
```
```{r}
#b
limmulti=lm(crim~.,Boston)
summary(limmulti)
#I choose p=0.005, thus we reject null hypothesis H0 : βj = 0 for dis, rad, mdev

```


```{r}
plot(stats[,1],coef(limmulti)[-1])
cbind(stats[,1],coef(limmulti)[-1])
#simple linear regression gave much larger coef for most of variables compare to multi linear regression. some even flip to positive or negative numbers.
```

```{r}

lm.fit1=lm(crim~poly(zn,3))
summary(lm.fit1)
lm.fit2=lm(crim~poly(indus,3))
summary(lm.fit2)
lm.fit3=lm(crim~poly(nox,3))
summary(lm.fit3)
lm.fit4=lm(crim~poly(rm,3))
summary(lm.fit4)
lm.fit5=lm(crim~poly(age,3))
summary(lm.fit5)
lm.fit6=lm(crim~poly(dis,3))
summary(lm.fit6)
lm.fit7=lm(crim~poly(rad,3))
summary(lm.fit7)
lm.fit8=lm(crim~poly(tax,3))
summary(lm.fit8)
lm.fit9=lm(crim~poly(ptratio,3))
summary(lm.fit9)
lm.fit10=lm(crim~poly(black,3))
summary(lm.fit10)
lm.fit11=lm(crim~poly(lstat,3))
summary(lm.fit11)
lm.fit12=lm(crim~poly(medv,3))
summary(lm.fit12)
#Yes, there is evidence of non-linear association for many of the predictors. crim vs dis, crim, medv
```
```{r}
## Chapter 6 question 9
rm(list=ls())
data(College,package="ISLR")
n<-nrow(College)
```


```{r}
#9(a)
set.seed(1)
train <- sample(1:n, n/2) #split the sample and testing into half and half
test <- (-train)
y.test <- College$Apps[test]
y.train <- College$Apps[train]
ref.err<-mean((mean(y.test)-y.test)^2)
ref.err
```

```{r}
#9(b)
#fit a linear model using least square on the training set and report the test error obtained
lm.mod <- lm(Apps ~ ., data=College[train,])
lm.pred <- predict(lm.mod, College[test,])
lm.err<-mean((lm.pred-y.test)^2)
lm.err
```
```{r}
#9(c)
#fit a ridge regression model on the training set with lambda chosen by cross validation 
set.seed(1)
library(glmnet)
x.mod <- model.matrix(Apps ~ ., data=College)[,-1]
ridge.mod.cv<-cv.glmnet(x.mod[train,],y.train,alpha=0)
ridge.best.lam <- ridge.mod.cv$lambda.min
ridge.mod <- glmnet(x.mod[train,],y.train,alpha=0)
ridge.pred <- predict(ridge.mod,newx=x.mod[test,],s=ridge.best.lam)
ridge.err<-mean((ridge.pred-y.test)^2)
ridge.err
```
```{r}
#9(d)
#fit a lasso model on the training set, with lambda chosen by cross validation.
set.seed(1)
x.mod <- model.matrix(Apps ~ ., data=College)[,-1]
lasso.mod.cv <- cv.glmnet(x.mod[train,],y.train,alpha=1)
lasso.best.lam <- lasso.mod.cv$lambda.min
lasso.mod <- glmnet(x.mod[train,],y.train,alpha=1)
lasso.pred <- predict(lasso.mod,newx=x.mod[test,],s=lasso.best.lam)
(lasso.err<-mean((lasso.pred-y.test)^2))
```
```{r}
##9(e) fit a PCR model on training set, with M chosen by cross validation
library(pls)
set.seed(1)
pcr.mod <- pcr(Apps ~ ., data=College, subset=train, scale=TRUE, validation="CV")
validationplot(pcr.mod,val.type="MSEP")
```


```{r}
summary(pcr.mod)
```
```{r}
pcr.pred <- predict(pcr.mod,College[test,],ncomp=16)
pcr.err<-mean((pcr.pred-y.test)^2)
pcr.err
#17 components considered
```

```{r}
##9(f)
library(pls)
set.seed(1)
pls.mod <- plsr(Apps ~ ., data=College, subset=train, validation="CV")
validationplot(pls.mod, val.type="MSEP")
#roughly the same CV after 4 components
```
```{r}
summary(pls.mod)
pls.pred <- predict(pls.mod,College[test,],ncomp=4)
pls.err<-mean((pls.pred-y.test)^2)
```
```{r}
#9(g)
rbind(ref.err,lm.err,ridge.err,lasso.err,pcr.err,pls.err)
#as we can see lasso nd ridge performed better than PCR and PLS, linear model  performed better than PCR and PLS
#Ridge was the best
```

## Chapter 6 question 11
```{r}
rm(list=ls())
data(Boston,package="MASS")
head(Boston)
Boston.mat <- model.matrix(crim ~ ., Boston)
```

## split the set into test and training
```{r}
set.seed(1)
train<-sample.int(nrow(Boston),size=nrow(Boston)*.5)
test<--train
y.train <- Boston$crim[train]
y.test <- Boston$crim[test]
```

## linear models, use best subsets to select the best train set using BIC
## then get the MSE on the test set

```{r}
require(leaps)
full.fit <- regsubsets(crim ~ ., data=Boston[train,],nvmax=ncol(Boston))
lm.best.coef <- coef(full.fit,id=which.min(summary(full.fit)$bic))
lm.pred <- Boston.mat[test,names(lm.best.coef)]%*%lm.best.coef
lm.err <- mean((lm.pred-y.test)^2)
lm.err
```

```{r}
full.lm.mod <- lm(crim ~ ., Boston, subset=train)
lm.full.pred <- predict(full.lm.mod, Boston[test,])
lm.full.err <- mean((lm.full.pred - y.test)^2)
lm.full.err
```
## Ridge and Lasso using CV
```{r}
library(glmnet)
runGlmNet <- function(alpha) {
  set.seed(500)
  cv <- cv.glmnet(Boston.mat[train,],y.train,alpha=alpha)
  best.lam <- cv$lambda.min
  mod <- glmnet(Boston.mat[train,],y.train,alpha=alpha)
  pred <- predict(mod,newx=Boston.mat[test,],s=best.lam)
  err<-mean((pred-y.test)^2)
  list(mod=mod,cv=cv,best.lam=best.lam,err=err)
}
# RIDGE
ridge.mod<-runGlmNet(0)
ridge.mod$err
```
```{r}
#Lasso
lasso.mod<-runGlmNet(1)
lasso.mod$err
```
## PCR 13 components looks good
```{r}
library(pls)
set.seed(500)
pcr.mod <- pcr(crim~.,data=Boston,subset=train,scale=TRUE,validation="CV")
summary(pcr.mod)
```
```{r}
validationplot(pcr.mod,val.type="MSEP")
```
```{r}
pcr.pred <- predict(pcr.mod,Boston[test,],ncomp=9)
pcr.err <- mean((pcr.pred-y.test)^2)
```
## to summarize, ridge model performed the best with lowest MRSE, followed by Lasso, then a linear regression
## best subset did not improve on the full lm either using validation set approach
```{r}
lasso.err <- lasso.mod$err
ridge.err <- ridge.mod$err
rbind(lm.err, lm.full.err, ridge.err, lasso.err, pcr.err)
```
## Chapter 4 question 10
```{r}
package="ISLR"
data(Weekly,package="ISLR")
summary(Weekly)
```
```{r}
cor(Weekly[,-c(1,9)])
```
## all pairwise comparisons of the predictors with the color denoting the direction. almost no trend here
```{r}
pairs(Weekly[-(8:9)],col=Weekly$Direction)
```
## Plotting the predictors against the `Today` variable. no trend here
```{r}
par(mfcol=c(3,2))
predictors <- c(paste0("Lag",1:5),"Volume")
for (p in predictors){
  plot(Weekly[,p],Weekly[,"Today"],
       ylab="Today",
       xlab=p,
       col=Weekly[,"Direction"])
}
```
## 10(b)

```{r}
glm.fit <- glm(Direction ~ Lag1 + Lag2 + Lag3 + Lag4 + Lag5 + Volume,data=Weekly, family=binomial)
summary(glm.fit)
```
## only lag 2 is statistically significant, dont really do anything for us here. since we got 6 predictors
## 10(c)

```{r}
glm.probs <- predict(glm.fit,type="response")
glm.pred <- rep("Down",nrow(Weekly))
glm.pred[glm.probs > .5] <- "Up"
table(glm.pred,Weekly$Direction) #confusion table
```
## the logistic regression is making false positive and false negative prediction a lot. almost a 50/50 flip coin.

## 10(d)
```{r}
train.inds <- Weekly$Year <= 2008
train.data <- Weekly[train.inds,]
test.data <- Weekly[!train.inds,]
test.n <- nrow(test.data)
lag2.mod <- glm(Direction ~ Lag2, data=Weekly, family=binomial, subset=train.inds)
summary(lag2.mod)
```

```{r}
lag2.pred <- rep("Down",test.n)
lag2.probs <- predict(glm.fit,test.data,type="response")
lag2.pred[lag2.probs>.5] <- "Up"
table(lag2.pred,test.data$Direction)
```
```{r}
sum(lag2.pred==test.data$Direction)/test.n
```
## over all correct prediction rate is 0.625. confusion matrix shows a quantifiable improvement.


## 10(g)
```{r}
library(class)
set.seed(1)
train.X <- as.matrix(train.data[,"Lag2"])
train.Y <- as.matrix(train.data[,"Direction"])
test.X <- as.matrix(test.data[,"Lag2"])
test.Y <- as.matrix(test.data[,"Direction"])
lag2.knn.pred <- knn(train.X,test.X,train.Y,k=1)
table(lag2.knn.pred,test.Y)
```
```{r}
sum(lag2.knn.pred == test.Y)/test.n
```
## K=1 is noisy, it is almost a flip coin. 

## 10(h)
## the logistic regression model using a training data period from 1990 to 2008, with Lag2 as the only predictorgives us the best prediction

## 10(i)
## let's play with KNN value

```{r}
k.vals <- 1:50
err <- double(50)
for (k in k.vals){
  train.X <- as.matrix(train.data[,"Lag2"])
  train.Y <- as.matrix(train.data[,"Direction"])
  test.X <- as.matrix(test.data[,"Lag2"])
  test.Y <- as.matrix(test.data[,"Direction"])
  lag2.knn.pred <- knn(train.X,test.X,train.Y,k=k)
  table(lag2.knn.pred,test.Y)
  err[k]<-sum(lag2.knn.pred == test.Y)/test.n
}
plot(k.vals,err,type="b")
```

## k=1 gives the best result on the test data.
Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.


